---
title: "R Notebook-Ants in Hengduan Mountains"
author: "Cong Liu"
output: html_notebook
---
####This R notebook includes all the analyses of Ants in Hengsuan Mountains project

#####PART1: Taxonomic and phylogenetic analyses of all sampling sites, including taxonomic beta diversity, phylogenetic alpha and beta diversities.

**Part1.1: Getting the phylogeny for our study**
```{r}
# Check if the taxa of community is in current phylogeny
require(phylotools)
tree<-read.tree("lognormal_l24.tre") # This is the global ant phylogeny (15k)
my_list<-read.csv("species_list.csv",row.names=1) # The species list from our study
label<-tree$tip.label
setdiff(label,my_list)
for (i in 1:128) {
  if (my_list[i,2] %in% label){
    next
  }else {
    print (my_list[i,2])
  }
}
```
Randomly replace the taxa which are not in the phylogeny. For example, we have three Acropyga species which are not in the current phylogeny, we need to replace them with three randomly Acropygra from the phylogeny. We need update our species list (not showing here).
```{r}
sample(grep("Acropyga",label,value = T),3) # Randomly sample three Acroyga species from the phylogeny.
```

Make a sub-phylogeny of our ant species
```{r}
require("geiger")
my_list<-read.csv("species_list.csv",row.names=1)
tree2<-treedata(tree,my_list)$phy
write.tree(tree2,file="finaltree.tre")
```
**Part1.2: Calculation of phylogeny alpha diveristy**
```{r}
require(picante)
phylogeny<-read.tree("finaltree.tre") # the phylogeny we generate during the first step.
comm<-read.csv("comm_all_label.csv",row.names=1) # Community data (present-absent matrix) with species name updated
## mean pairwide distance (MPD)== NRI
nri<-ses.mpd(comm,cophenetic(phylogeny),null.model = "independentswap",abundance.weighted = F,runs=1000,iterations = 1000)
write.csv(nri,file="nri.csv")
## mean nearest taxon distance (MNTD)==NTI
nti<-ses.mntd(comm,cophenetic(phylogeny),null.model = "independentswap",abundance.weighted = F,runs=1000,iterations = 1000)
write.csv(nti,file="nti.csv")
```
**Part1.3: Calculation of taxnomic beta diversity**  
Taxonomic beta diversity calculation was based on recent framework that partition beta diversity into turnover and nestedness.
```{r}
# cauculate taxonomic beta diversity (turnover and nestedness)
library(betapart)
beta_all<-function(x){
  beta.pair(randomizeMatrix(x,null.model = "independentswap"),index.family = "sorensen")
}
obs<-beta.pair(comm,index.family = "sorensen")
# Cauculate turnover (sim)
null.sim<-replicate(1000,as.matrix(beta_all(comm)$beta.sim))
null.sim.mean<-apply(null.sim,c(1,2),mean,na.rm=T)
null.sim.sd<-apply(null.sim,c(1,2),sd,na.rm=T)
ses.sim<-(as.matrix(obs$beta.sim)-null.sim.mean)/null.sim.sd
write.csv(ses.sim,file="ses_sim.csv")
  
# Cauculate nestedness (nest)
null.nest<-replicate(1000,as.matrix(beta_all(comm)$beta.sne))
null.nest.mean<-apply(null.nest,c(1,2),mean,na.rm=T)
null.nest.sd<-apply(null.nest,c(1,2),sd,na.rm=T)
ses.nest<-(as.matrix(obs$beta.sne)-null.nest.mean)/null.nest.sd
write.csv(ses.nest,file="ses_nest.csv")

# Cauculate total (total)
null.total<-replicate(1000,as.matrix(beta_all(comm)$beta.sor))
null.total.mean<-apply(null.total,c(1,2),mean,na.rm=T)
null.total.sd<-apply(null.total,c(1,2),sd,na.rm=T)
ses.total<-(as.matrix(obs$beta.sor)-null.total.mean)/null.total.sd
write.csv(ses.total,file="ses_total.csv")

# Calculate proportion of turnover components
sim.porportion<-(obs$beta.sim)/(obs$beta.sor)
sim.porportion<-as.matrix(sim.porportion)
sim.porportion[!lower.tri(sim.porportion)]<-NA
dim(sim.porportion)<-c(dim(sim.porportion)[1]*dim(sim.porportion)[2], 1)
sim.porportion<-sim.porportion[complete.cases(sim.porportion),]
sim.porportion<-as.data.frame(sim.porportion)
write.csv(sim.porportion,file="sim.porportion.csv")
```
**Part1.4: Calculation of phylogenetic beta diversities**
```{r}
#partitioning phylogenetic beta into turnover and nestedness
require(betapart)
phy_beta_all<-function(x){
  phylo.beta.pair(randomizeMatrix(x,null.model = "independentswap"),phylogeny,index.family = "sorensen")
}
obs_phylo_beta<-phylo.beta.pair(comm,phylogeny,index.family = "sorensen")
## cauculate turnover (sim)
phylo_null.sim<-replicate(1000,as.matrix(phy_beta_all(comm)$phylo.beta.sim))
phylo_null.sim.mean<-apply(phylo_null.sim,c(1,2),mean,na.rm=T)
phylo_null.sim.sd<-apply(phylo_null.sim,c(1,2),sd,na.rm=T)
ses_phylo.sim<-(as.matrix(obs_phylo_beta$phylo.beta.sim)-phylo_null.sim.mean)/phylo_null.sim.sd
write.csv(ses_phylo.sim,file="ses_phylo_sim.csv")

## cauculate nestedness (nest)
phylo_null.nest<-replicate(1000,as.matrix(phy_beta_all(comm)$phylo.beta.sne))
phylo_null.nest.mean<-apply(phylo_null.nest,c(1,2),mean,na.rm=T)
phylo_null.nest.sd<-apply(phylo_null.nest,c(1,2),sd,na.rm=T)
ses_phylo.nest<-(as.matrix(obs_phylo_beta$phylo.beta.sne)-phylo_null.nest.mean)/phylo_null.nest.sd
write.csv(ses_phylo.nest,file="ses_phylo_nest.csv")

## cauculate total (total)
phylo_null.total<-replicate(1000,as.matrix(phy_beta_all(comm)$phylo.beta.sor))
phylo_null.total.mean<-apply(phylo_null.total,c(1,2),mean,na.rm=T)
phylo_null.total.sd<-apply(phylo_null.total,c(1,2),sd,na.rm=T)
ses_phylo.total<-(as.matrix(obs_phylo_beta$phylo.beta.sor)-phylo_null.total.mean)/phylo_null.total.sd
write.csv(ses_phylo.total,file="ses_phylo_total.csv")

# calculate proportion of phylogenetic turnover components
sim.porportion<-(obs_phylo_beta$phylo.beta.sim)/(obs_phylo_beta$phylo.beta.sor)
sim.porportion<-as.matrix(sim.porportion)
sim.porportion[!lower.tri(sim.porportion)]<-NA
dim(sim.porportion)<-c(dim(sim.porportion)[1]*dim(sim.porportion)[2], 1)
sim.porportion<-sim.porportion[complete.cases(sim.porportion),] ###
sim.porportion<-as.data.frame(sim.porportion)
write.csv(sim.porportion,file="sim.porportion_phylo.csv")
```


#####PART2: Processing climatic data. 
**Part2.1: Climatic variables selection**  
Calculate the correlation between climate data and alpha diversities and remove weak explianatory variables (p<0.1)
```{r}
env<-read.csv("environmental_data.csv",row.names=1)
alpha<-read.csv("alpha.csv",row.names=1)
cor_climate<-matrix(nrow = 19,ncol = 2)
row.names(cor_climate)<-colnames(env)
colnames(cor_climate)<-c("SR","NRI")
for (i in 1:19){
  cor_climate[i,1]<-round(cor.test(env[,i],alpha[,2])$estimate,digits = 4)
  cor_climate[i,2]<-round(cor.test(env[,i],alpha[,3])$estimate,digits = 4)
}
write.csv(cor_climate,file="cor.climate.csv")
```

Calculate the correlation between climate variables. If r>0.7, then remove the variables that with poorer explianatoty
```{r}
cor_climate2<-cor(env,method = "spearman")
write.csv(cor_climate2,file="cor_climate2.csv") # only bio1, bio2, bio3 for temperature and bio12, bio15 for precipitation left
```

**Part2.2: PCA of selected climatic variables**  
Running PCA for both temperature and precipitation variavles and select only PC1s for presenting tem and precip variables.

```{r}
climate<-read.csv("climate_reduced.csv",row.names=1)
climate_pca<-matrix(nrow=55,ncol = 2)
row.names(climate_pca)<-rownames(climate)
colnames(climate_pca)<-c("tem","prec")
tem<-climate[,c(1,2,3)]
prec<-climate[,c(4,5)]
tem_pca<-princomp(tem)
prec_pca<-princomp(prec)
summary(tem_pca)
summary(prec_pca)
climate_pca[,1]<-tem_pca$scores[,1]
climate_pca[,2]<-prec_pca$scores[,1]
write.csv(climate_pca,file="climate_pca.csv")
```

**Part2.3: Making distance matrix for climatic data (PC1s of both tem and precip)**  
```{r}
# make a distance matrix of climate pca data (Euclidean)
climate_dis<-dist(scale(climate_pca,center = T,scale = T))
write.csv(as.matrix(climate_dis),file="climate_dis.csv")

# cover matrix into one column
matrix1<-as.matrix(climate_dis)
matrix1[!lower.tri(matrix1)]<-NA
dim(matrix1)<-c(dim(matrix1)[1]*dim(matrix1)[2], 1)
matrix1<-matrix1[complete.cases(matrix1),] ###
matrix1<-as.data.frame(matrix1)
write.csv(matrix1,file="climate_dis.csv")
```

#####PART3: Statistics, GAM and more

**Part3.1: For alpha diversity**  
```{r}
require(mgcv)
alpha<-read.csv("alpha.csv")

# Species richness
gam1<-gam(alpha$ntaxa~tem+prec+s(Lat,Lon),family = "poisson",data=alpha)
gam2<-gam(alpha$ntaxa~s(alpha$tem),family = "poisson",data=alpha)
gam3<-gam(alpha$ntaxa~s(alpha$prec),family = "poisson",data=alpha)
gam4<-gam(alpha$ntaxa~s(alpha$elevation)+s(Lat,Lon),family = "poisson",data=alpha)
gam5<-gam(alpha$ntaxa~s(alpha$tem)+s(alpha$prec)+s(alpha$elevation),family = "poisson",data=alpha)
gam6<-gam(alpha$ntaxa~s(alpha$tem)+s(alpha$elevation),family = "poisson",data=alpha)
gam7<-gam(alpha$ntaxa~s(alpha$prec)+s(alpha$elevation),family = "poisson",data=alpha)
summary(gam1)
summary(gam2)
summary(gam3)
summary(gam4)
summary(gam5)
summary(gam6)
summary(gam7)

#NRI
gam8<-gam(alpha$nri~s(alpha$tem),data=alpha)
gam9<-gam(alpha$nri~s(alpha$prec),data=alpha)
gam10<-gam(alpha$nri~s(alpha$elevation)+s(Lat,Lon),data=alpha)
gam11<-gam(alpha$nri~s(alpha$elevation)+s(alpha$tem),data=alpha)
gam12<-gam(alpha$nri~s(alpha$elevation)+s(alpha$prec),data=alpha)
gam13<-gam(alpha$nri~s(alpha$tem)+s(alpha$prec),data=alpha)
gam14<-gam(alpha$nri~s(alpha$tem)+s(alpha$prec)+s(alpha$elevation),data=alpha)
summary(gam8)
summary(gam9)
summary(gam10)
summary(gam11)
summary(gam12)
summary(gam13)
summary(gam14)
```
**Part3.1: For beta diversity** 
```{r}
beta<-read.csv("beta.csv")

# Taxonomic beta diversity
gam15<-gam(TBD_total.ses~s(distance),data=beta)
gam15_1<-gam(TBD_total.ses~s(cost_bin3),data=beta)
gam16<-gam(TBD_total.ses~s(climate_distance),data=beta)
gam17<-gam(TBD_total.ses~s(climate_distance)+s(distance),data=beta)
gam17_1<-gam(TBD_total.ses~s(climate_distance)+s(cost_bin3),data=beta)

gam18<-gam(TBD_turn.ses~s(distance),data=beta)
gam19<-gam(TBD_turn.ses~s(climate_distance),data=beta)
gam20<-gam(TBD_turn.ses~s(climate_distance)+s(distance),data=beta)

gam21<-gam(TBD_nest.ses~s(distance),data=beta)
gam22<-gam(TBD_nest.ses~s(climate_distance),data=beta)
gam23<-gam(TBD_nest.ses~s(climate_distance)+s(distance),data=beta)

summary(gam15)
summary(gam15_1)
summary(gam16)
summary(gam17)
summary(gam17_1)
summary(gam18)
summary(gam19)
summary(gam20)
summary(gam21)
summary(gam22)
summary(gam23)

# Phylogenetic beta diversity
gam24<-gam(PBD_total.ses~s(distance),data=beta)
gam25<-gam(PBD_total.ses~s(climate_distance),data=beta)
gam26<-gam(PBD_total.ses~s(climate_distance)+s(distance),data=beta)

gam27<-gam(PBD_turn.ses~s(distance),data=beta)
gam28<-gam(PBD_turn.ses~s(climate_distance),data=beta)
gam29<-gam(PBD_turn.ses~s(climate_distance)+s(distance),data=beta)

gam30<-gam(PBD_nest.ses~s(distance),data=beta)
gam31<-gam(PBD_nest.ses~s(climate_distance),data=beta)
gam32<-gam(PBD_nest.ses~s(climate_distance)+s(distance),data=beta)

summary(gam24)
summary(gam25)
summary(gam26)
summary(gam27)
summary(gam28)
summary(gam29)
summary(gam30)
summary(gam31)
summary(gam32)
```


#####PART4: Elevational connectivity
**Here are analyses related to elevational connectivity**  
**Part4.1: For 3000 randomly generated site (simulation), Calculate ele_dis, ele_ave, geo distance, and cost distance for all the pairs within 400m buffer**  
```{r}
# Make matrix of elevation distance,average elevation, and input cost distance between pairs of all sites
elevation1<-read.csv("site_elevation_random.csv",header = F,row.names = 1)
elevation_dist<-t(outer(elevation1[,1],elevation1[,1],'-'))
row.names(elevation_dist)<-row.names(elevation1)
colnames(elevation_dist)<-row.names(elevation1)
elevation_dist[!lower.tri(elevation_dist)]<-NA

elevation_ave<-(t(outer(elevation1[,1],elevation1[,1],'+')))/2
row.names(elevation_ave)<-row.names(elevation1)
colnames(elevation_ave)<-row.names(elevation1)
elevation_ave[!lower.tri(elevation_ave)]<-NA

cost<-as.matrix(read.csv("CostDistResult_random.csv",row.names = 1))
cost[!lower.tri(cost)]<-NA

#convert matrice into one column
dim(elevation_dist)<-c(dim(elevation_dist)[1]*dim(elevation_dist)[2], 1)
elevation_dist<-elevation_dist[complete.cases(elevation_dist),]

dim(elevation_ave)<-c(dim(elevation_ave)[1]*dim(elevation_ave)[2], 1)
elevation_ave<-elevation_ave[complete.cases(elevation_ave),]

dim(cost)<-c(dim(cost)[1]*dim(cost)[2], 1)
cost<-cost[complete.cases(cost),]

# Output all ele_dis, ele_ave, and cost distance of selected pairs (ele_dis<400m, 400m buffer)
result<-matrix(nrow=4498500,ncol=5)
colnames(result)<-c("ele_dis","ele_ave","cost_dis","tbd","pbd")
a=1
for (i in 1:4498500){
  if (abs(elevation_dist[i])<=400){
    result[a,1]=elevation_dist[i]
    result[a,2]=elevation_ave[i]
    result[a,3]=cost[i]
    a=a+1
  }
}
write.csv(result,file="summary_random.csv")
```

**Part4.2: For our real sampling site, Calculate ele_dis, ele_ave, geo distance, and cost distance for all the pairs within 400m buffer**
```{r}
# Make matrix of elevation distance,average elevation, and input cost distance between pairs of all sites
elevation1<-read.csv("site_elevation.csv",header = F,row.names = 1)
elevation_dist<-t(outer(elevation1[,1],elevation1[,1],'-'))
row.names(elevation_dist)<-row.names(elevation1)
colnames(elevation_dist)<-row.names(elevation1)
elevation_dist[!lower.tri(elevation_dist)]<-NA

elevation_ave<-(t(outer(elevation1[,1],elevation1[,1],'+')))/2
row.names(elevation_ave)<-row.names(elevation1)
colnames(elevation_ave)<-row.names(elevation1)
elevation_ave[!lower.tri(elevation_ave)]<-NA

cost<-as.matrix(read.csv("CostDistResult_bin500.csv",row.names = 1))
cost[!lower.tri(cost)]<-NA
geo_dis<-as.matrix(read.csv("ditance.csv",row.names = 1))
geo_dis[!lower.tri(geo_dis)]<-NA
#convert matrice into one column
dim(elevation_dist)<-c(dim(elevation_dist)[1]*dim(elevation_dist)[2], 1)
elevation_dist<-elevation_dist[complete.cases(elevation_dist),]

dim(elevation_ave)<-c(dim(elevation_ave)[1]*dim(elevation_ave)[2], 1)
elevation_ave<-elevation_ave[complete.cases(elevation_ave),]

dim(cost)<-c(dim(cost)[1]*dim(cost)[2], 1)
cost<-cost[complete.cases(cost),]

dim(geo_dis)<-c(dim(geo_dis)[1]*dim(geo_dis)[2], 1)
geo_dis<-geo_dis[complete.cases(geo_dis),]
# Output all ele_dis, ele_ave, and cost distance of selected pairs (ele_dis<400m)
result<-matrix(nrow=1485,ncol=6)
colnames(result)<-c("ele_dis","ele_ave","cost_dis","geo_dis","tbd","pbd")
a=1
for (i in 1:1485){
  if (abs(elevation_dist[i])<=400){
    result[a,1]=elevation_dist[i]
    result[a,2]=elevation_ave[i]
    result[a,3]=cost[i]
    result[a,4]=geo_dis[i]
    a=a+1
  }
}
write.csv(result,file="summary_500.csv")
```

**Part4.3: For our real sampling site, Calculating TBD and PBD for all the pairs within 400m buffer.**  

* Part4.3.1: Access the elevational range of each species (for define species pool within each elevational buffer).
```{r}
comm<-as.matrix(read.csv("comm_all_label.csv",row.names=1))
elevation<-read.csv("site_elevation.csv",header=F,row.names = 1)
result<-matrix(ncol = 127, nrow = 55)
colnames(result)<-colnames(comm)
for (i in 1:127){
  a=1
  for (j in 1:55){
    if (comm[j,i]==1){
      result[a,i]=elevation[row.names(elevation)==row.names(comm)[j],1]
      a=a+1
    }
  }
}

min_ele<-c()
max_ele<-c()
for (i in 1:127){
  min_ele<-append(min_ele,min(result[,i],na.rm = T))
  max_ele<-append(max_ele,max(result[,i],na.rm = T))
}
id<-colnames(comm)
elevation_range<-data.frame(id,min_ele,max_ele)

# Redefine species elevational range. for those species only been collected in one site, we define their elevational range as +-200m, +-150m, +-250m
for (i in 1:127){
  if(elevation_range$min_ele[i]==elevation_range$max_ele[i]){
    elevation_range$min_ele[i]=elevation_range$min_ele[i]-200
    elevation_range$max_ele[i]=elevation_range$max_ele[i]+200
  }
}
write.csv(elevation_range,file="elevational_range_400.csv")
```
* Part4.3.2: Get sites names that in our analyse ncol=249 for 300m band, ncol=332 for 400m band, ncol= 407 for 500m band.
```{r}
elevation1<-read.csv("site_elevation.csv",header = F,row.names = 1)
elevation_dist<-t(outer(elevation1[,1],elevation1[,1],'-'))
row.names(elevation_dist)<-row.names(elevation1)
colnames(elevation_dist)<-row.names(elevation1)
elevation_dist[!lower.tri(elevation_dist)]<-NA

elevation_ave<-(t(outer(elevation1[,1],elevation1[,1],'+')))/2
row.names(elevation_ave)<-row.names(elevation1)
colnames(elevation_ave)<-row.names(elevation1)
elevation_ave[!lower.tri(elevation_ave)]<-NA
site<-matrix(ncol = 332,nrow = 2) #ncol= the number of pairs for the defined elevational band
a=1
for (i in 1:55){
  for (j in 1:55){
    if (is.na(elevation_dist[j,i])) next
    if (abs(elevation_dist[j,i])<=400){
      site[1,a]=colnames(elevation_dist)[i]
      site[2,a]=row.names(elevation_dist)[j]
      a=a+1
    }
  }
}
#get the average elevation of each pair for getting species pool
results2<-read.csv("summary_400.csv")
elevation_range<-read.csv("elevational_range_400.csv",stringsAsFactors = F)
```

* Part4.3.3 Calculate TBD among all sites that within 400m elevational buffer.
```{r}
require(picante)
require(betapart)
beta_all<-function(x){
  beta.pair(randomizeMatrix(x,null.model = "richness"),index.family = "sorensen")
}
result3<-matrix(nrow=1,ncol=332) #ncol= the number of pairs for the defined elevational band
for (i in 1:332){
  comm<-read.csv("comm_all_label.csv",row.names=1)
  comm<-comm[row.names(comm)%in% site[,i],]
  sp<-c()
  for (x in 1:127){ #the number here is the number of species
    if (results2$ele_ave[i]>=elevation_range$min_ele[x]&results2$ele_ave[i]<=elevation_range$max_ele[x]){
      sp<-append(sp,elevation_range$id[x])
    }
  }
  comm<-comm[,colnames(comm)%in% sp]
  obs<-beta.pair(comm,index.family = "sorensen")
  null.turn<-replicate(1000,as.matrix(beta_all(comm)$beta.sim))
  null.turn.mean<-apply(null.turn,c(1,2),mean,na.rm=T)
  null.turn.sd<-apply(null.turn,c(1,2),sd,na.rm=T)
  ses.turn<-(as.matrix(obs$beta.sim)-null.turn.mean)/null.turn.sd
  ses.turn[!lower.tri(ses.turn)]<-NA
  dim(ses.turn)<-c(dim(ses.turn)[1]*dim(ses.turn)[2], 1)
  ses.turn<-ses.turn[complete.cases(ses.turn),]
  result3[1,i]=ses.turn
  print (paste0(i/332*100,"%"))
  }
write.csv(result3,file="tbd_400.csv")
```

* Part4.3.4 Calculate PBD among all sites that within 400m elevational buffer.
```{r}
library(phylotools)
library(geiger)
phy_beta<-function(x,y){
  phylo.beta.pair(randomizeMatrix(x,null.model = "richness"),y,index.family = "sorensen")
}
phylogeny<-read.tree("/Users/Liu/Dropbox (OIST)/projects/xizang ant/R_new/finaltree.tre")
result3<-matrix(nrow=1,ncol=332)
for (i in 1:332){
  comm<-read.csv("comm_all_label.csv",row.names=1)
  comm<-comm[row.names(comm)%in% site[,i],]
  sp<-c()
  for (x in 1:127){
    if (results2$ele_ave[i]>=elevation_range$min_ele[x]&results2$ele_ave[i]<=elevation_range$max_ele[x]){
      sp<-append(sp,elevation_range$id[x])
    }
  }
  comm<-comm[,colnames(comm)%in% sp]
  obs_phylo<-phylo.beta.pair(comm,treedata(phylogeny,t(comm))$phy,index.family = "sorensen")
  phylo_null<-replicate(1000,as.matrix(phy_beta(comm,treedata(phylogeny,t(comm))$phy)$phylo.beta.sor))
  phylo_null.mean<-apply(phylo_null,c(1,2),mean,na.rm=T)
  phylo_null.sd<-apply(phylo_null,c(1,2),sd,na.rm=T)
  ses_phylo<-(as.matrix(obs_phylo$phylo.beta.sor)-phylo_null.mean)/phylo_null.sd
  
  ses_phylo[!lower.tri(ses_phylo)]<-NA
  dim(ses_phylo)<-c(dim(ses_phylo)[1]*dim(ses_phylo)[2], 1)
  ses_phylo<-ses_phylo[complete.cases(ses_phylo),]
  result3[1,i]=ses_phylo
  print (paste0(i/332*100,"%"))
  
}
write.csv(result3,file="pbd_400.csv")
```

#####PART5: Plotting
**Part5.1: Alpha diversity**
```{r}
require(ggplot2)
require(plotly)
require(gridExtra)
alpha<-read.csv("alpha.csv",row.names=1)
mytheme<-theme(axis.title=element_text(size=15, lineheight=.9, family="Helvetica",face="bold", colour="black"))+theme(axis.text=element_text(size=12, lineheight=.9,family="Helvetica",face="bold", colour="black"))

nri<-ggplot(alpha,aes(x=alpha$elevation,y=alpha$nri,size=alpha$ntaxa,colour=as.factor(alpha$colour)))+geom_point(alpha=.8)+ylim(-3,3)+scale_size_area()+
mytheme+xlab("Elevation (m)")+ylab("-1XNRI")+geom_hline(yintercept=0,linetype="dashed",size=0.5)+theme(legend.position="none")+theme(axis.text=element_text(size=12, lineheight=.9,family="Helvetica",face="bold", colour="black"))+scale_color_manual(values = c("red","black","blue"))

sr_elev<-ggplot(aes(x=alpha$elevation, y=alpha$ntaxa), data=alpha) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Elevation (m)")+ylab("Species Richness")+mytheme 
# Output figure
tiff(filename = "figure1.tiff",width = 3000,height = 1350,units = "px",compression = "lzw",res = 300)
grid.arrange(sr_elev,nri,nrow=1)
dev.off()
sr_elev
nri
```
**Part5.2: Beta diversity**
```{r}
beta<-read.csv("beta.csv")

TBD_total<-ggplot(beta,aes(x=scale(beta$climate_distance,scale = T,center = F),y=beta$TBD_total.ses,colour=beta$distance))+geom_point()+xlab("Euclidean climate distance")+ylab("Taxonomic beta(total)")+geom_hline(yintercept=1.96,linetype="dashed",size=0.5)+geom_hline(yintercept=-1.96,linetype="dashed",size=0.5)+scale_size_area()+mytheme+theme(legend.position="none")+theme(axis.text=element_text(size=12, lineheight=.9,family="Helvetica",face="bold", colour="black"))+ylim(-7.5,7.5)

TBD_turn<-ggplot(beta,aes(x=scale(beta$climate_distance,scale = T,center = F),y=beta$TBD_turn.ses,colour=beta$distance))+geom_point()+xlab("Euclidean climate distance")+ylab("Taxonomic beta(turnover)")+geom_hline(yintercept=1.96,linetype="dashed",size=0.5)+geom_hline(yintercept=-1.96,linetype="dashed",size=0.5)+scale_size_area()+mytheme+theme(legend.position="none")+theme(axis.text=element_text(size=12, lineheight=.9,family="Helvetica",face="bold", colour="black"))+ylim(-7.5,7.5)

TBD_sne<-ggplot(beta,aes(x=scale(beta$climate_distance,scale = T,center = F),y=beta$TBD_nest.ses,colour=beta$distance))+geom_point()+xlab("Euclidean climate distance")+ylab("Taxonomic beta(nestedness)")+geom_hline(yintercept=1.96,linetype="dashed",size=0.5)+geom_hline(yintercept=-1.96,linetype="dashed",size=0.5)+scale_size_area()+mytheme+theme(legend.position=c(0.9,0.8))+labs(colour="Distance(km)")+theme(legend.title=element_text(size=10,lineheight=.9,family="Helvetica",face="bold", colour="black"))+theme(legend.background=element_blank())+theme(axis.text=element_text(size=12, lineheight=.9,family="Helvetica",face="bold", colour="black"))+ylim(-7.5,7.5)

PBD_total<-ggplot(beta,aes(x=scale(beta$climate_distance,scale = T,center = F),y=beta$PBD_total.ses,colour=beta$distance))+geom_point()+xlab("Euclidean climate distance")+ylab("Phylogenetic beta(total)")+geom_hline(yintercept=1.96,linetype="dashed",size=0.5)+geom_hline(yintercept=-1.96,linetype="dashed",size=0.5)+scale_size_area()+mytheme+theme(legend.position="none")+theme(axis.text=element_text(size=12, lineheight=.9,family="Helvetica",face="bold", colour="black"))+ylim(-7.5,7.5)

PBD_turn<-ggplot(beta,aes(x=scale(beta$climate_distance,scale = T,center = F),y=beta$PBD_turn.ses,colour=beta$distance))+geom_point()+xlab("Euclidean climate distance")+ylab("Phylogenetic beta(turnover)")+geom_hline(yintercept=1.96,linetype="dashed",size=0.5)+geom_hline(yintercept=-1.96,linetype="dashed",size=0.5)+scale_size_area()+mytheme+theme(legend.position="none")+theme(axis.text=element_text(size=12, lineheight=.9,family="Helvetica",face="bold", colour="black"))+ylim(-7.5,7.5)

PBD_sne<-ggplot(beta,aes(x=scale(beta$climate_distance,scale = T,center = F),y=beta$PBD_nest.ses,colour=beta$distance))+geom_point()+xlab("Euclidean climate distance")+ylab("Phylogenetic beta(nestedness)")+geom_hline(yintercept=1.96,linetype="dashed",size=0.5)+geom_hline(yintercept=-1.96,linetype="dashed",size=0.5)+scale_size_area()+mytheme+theme(legend.position=c(0.9,0.8))+labs(colour="Distance(km)")+theme(legend.title=element_text(size=10,lineheight=.9,family="Helvetica",face="bold", colour="black"))+theme(legend.background=element_blank())+theme(axis.text=element_text(size=12, lineheight=.9,family="Helvetica",face="bold", colour="black"))+ylim(-7.5,7.5)

tiff(filename = "figure2.tiff",width = 4500,height = 2700,units = "px",compression = "lzw",res = 300)
grid.arrange(TBD_total,TBD_turn,TBD_sne,PBD_total,PBD_turn,PBD_sne,nrow=2)
dev.off()
```

**Part5.3: plotting "proportion of total explained deviance for both beta diversities"**  
```{r}
r2<-read.csv("R2_partition.csv")
r2$type<-factor(r2$type,levels=c("Taxonomic beta","Phylogenetic beta"))
p1<-ggplot(r2,aes(x=beta,y=proportion2,fill=cat))+geom_bar(width=.7,stat = "identity",colour="black")+scale_fill_manual(values = c("black","white","grey70"))+facet_grid(.~type,scales = "free_x")
p1<-p1+mythem+ylab("Proportion of total explained deviance")+xlab("")+theme(strip.text = element_text(face="bold",family = "Helvetica", size=12))
p1<-p1+scale_x_discrete(breaks=c("A1","A2","A3","B1","B2","B3"),labels=c("SES_Total","SES_Turnover","SES_Nestedness","SES_Total","SES_Turnover","SES_Nestedness"))+theme(axis.text.x = element_text(angle=30, hjust=1, vjust=1))
p1<-p1+labs(fill="Explained by")+theme(legend.text=element_text(size=9,lineheight = .9,family = "Helvetica",face="bold",colour = "black"),legend.title=element_text(size=10, lineheight=.9, family="Helvetica",face="bold", colour="black"))
p1<-p1+guides(fill = guide_legend(keywidth = 0.5, keyheight = 0.5,title="Explained by:"))+theme(legend.background=element_rect(fill="white", colour="black"))+theme(legend.position=c(.8,.2))
tiff(filename = "figure6.tiff",width = 2000,height = 1700,units = "px",compression = "lzw",res = 300)
p1
dev.off()
```

**Part5.4: Plotting GAM**  

* Alpha diversity.
```{r}
# The fit of generalized additivemodels (GAM) with 95% confidencebands examining the individualrelationship between alpha diversities and variables
sr_tem<-ggplot(aes(x=alpha$tem, y=alpha$ntaxa), data=alpha) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Temperature (PC1)")+ylab("Species Richness")+mytheme 

sr_prec<-ggplot(aes(x=alpha$prec, y=alpha$ntaxa), data=alpha) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Precipitation (PC1)")+ylab("Species Richness")+mytheme 

sr_elev<-ggplot(aes(x=alpha$elevation, y=alpha$ntaxa), data=alpha) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Elevation (m)")+ylab("Species Richness")+mytheme 

nri_tem<-ggplot(aes(x=alpha$tem, y=alpha$nri), data=alpha) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Temperature (PC1)")+ylab("-1XNRI")+mytheme 

nri_prec<-ggplot(aes(x=alpha$prec, y=alpha$nri), data=alpha) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Precipitation (PC1)")+ylab("1XNRI")+mytheme 

nri_elev<-ggplot(aes(x=alpha$elevation, y=alpha$nri), data=alpha) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Elevation (m)")+ylab("1XNRI")+mytheme 
tiff(filename = "figure3.tiff",width = 4500,height = 2700,units = "px",compression = "lzw",res = 300)
grid.arrange(sr_tem,sr_prec,sr_elev,nri_tem,nri_prec,nri_elev,nrow=2)
dev.off()
```

* Beta diversity.
```{r}
# The fit of generalized additivemodels (GAM) with 95% confidencebands examining the individualrelationship between beta diversities and variables
climate_TBD_total<-ggplot(aes(x=scale(beta$climate_distance,scale = T,center = F), y=beta$TBD_total.ses), data=beta) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Euclidean climate distance")+ylab("TBD (SES_SOR)")+ylim(-7.5,7.5)+mytheme 

climate_TBD_turn<-ggplot(aes(x=scale(beta$climate_distance,scale = T,center = F), y=beta$TBD_turn.ses), data=beta) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Euclidean climate distance")+ylab("TBD (SES_SIM)")+ylim(-7.5,7.5)+mytheme 

climate_TBD_nest<-ggplot(aes(x=scale(beta$climate_distance,scale = T,center = F), y=beta$TBD_nest.ses), data=beta) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Euclidean climate distance")+ylab("TBD (SES_SNE)")+ylim(-7.5,7.5)+mytheme 

distance_TBD_total<-ggplot(aes(x=beta$distance, y=beta$TBD_total.ses), data=beta) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Geographic distance (km)")+ylab("TBD (SES_SOR)")+ylim(-7.5,7.5)+mytheme 

distance_TBD_turn<-ggplot(aes(x=beta$distance, y=beta$TBD_turn.ses), data=beta) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Geographic distance (km)")+ylab("TBD (SES_SIM)")+ylim(-7.5,7.5)+mytheme 

distance_TBD_nest<-ggplot(aes(x=beta$distance, y=beta$TBD_nest.ses), data=beta) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Geographic distance (km)")+ylab("TBD (SES_SNE)")+ylim(-7.5,7.5)+mytheme 

climate_PBD_total<-ggplot(aes(x=scale(beta$climate_distance,scale = T,center = F), y=beta$PBD_total.ses), data=beta) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Euclidean climate distance")+ylab("PBD (SES_SOR)")+ylim(-7.5,7.5)+mytheme 

climate_PBD_turn<-ggplot(aes(x=scale(beta$climate_distance,scale = T,center = F), y=beta$PBD_turn.ses), data=beta) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Euclidean climate distance")+ylab("PBD (SES_SIM)")+ylim(-7.5,7.5)+mytheme 

climate_PBD_nest<-ggplot(aes(x=scale(beta$climate_distance,scale = T,center = F), y=beta$PBD_nest.ses), data=beta) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Euclidean climate distance")+ylab("PBD (SES_SNE)")+ylim(-7.5,7.5)+mytheme 

distance_PBD_total<-ggplot(aes(x=beta$distance, y=beta$PBD_total.ses), data=beta) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Geographic distance (km)")+ylab("PBD (SES_SOR)")+ylim(-7.5,7.5)+mytheme 

distance_PBD_turn<-ggplot(aes(x=beta$distance, y=beta$PBD_turn.ses), data=beta) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Geographic distance (km)")+ylab("PBD (SES_SIM)")+ylim(-7.5,7.5)+mytheme 

distance_PBD_nest<-ggplot(aes(x=beta$distance, y=beta$PBD_nest.ses), data=beta) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr"))+xlab("Geographic distance (km)")+ylab("PBD (SES_SNE)")+ylim(-7.5,7.5)+mytheme 

tiff(filename = "figure4.tiff",width = 4500,height = 5400,units = "px",compression = "lzw",res = 300)
grid.arrange(climate_TBD_total,climate_TBD_turn,climate_TBD_nest,distance_TBD_total,distance_TBD_turn,distance_TBD_nest,climate_PBD_total,climate_PBD_turn,climate_PBD_nest,distance_PBD_total,distance_PBD_turn,distance_PBD_nest,nrow=4)
dev.off()

#plot vis.gam plot for beta diversities
gam_1<-gam(TBD_total.ses~te(climate_distance1,distance,k=3),data=beta)
tiff(filename = "figure5-1.tiff",width = 1500,height = 1500,units = "px",compression = "lzw",res = 300)
vis.gam(gam_1,type='response', plot.type='persp', theta=-40,n.grid=1000, border=NA,xlab="",ylab="",zlab="",ticktype="detailed")
dev.off()

gam_2<-gam(TBD_turn.ses~te(climate_distance1,distance,k=3),data=beta)
tiff(filename = "figure5-2.tiff",width = 1500,height = 1500,units = "px",compression = "lzw",res = 300)
vis.gam(gam_2,type='response', plot.type='persp', theta=-40,n.grid=1000, border=NA,xlab="",ylab="",zlab="",ticktype="detailed")
dev.off()

gam_3<-gam(TBD_nest.ses~te(climate_distance1,distance,k=3),data=beta)
tiff(filename = "figure5-3.tiff",width = 1500,height = 1500,units = "px",compression = "lzw",res = 300)
vis.gam(gam_3,type='response', plot.type='persp', theta=-40,n.grid=1000, border=NA,xlab="",ylab="",zlab="",ticktype="detailed")
dev.off()

gam_4<-gam(PBD_total.ses~te(climate_distance1,distance,k=3),data=beta)
tiff(filename = "figure5-4.tiff",width = 1500,height = 1500,units = "px",compression = "lzw",res = 300)
vis.gam(gam_4,type='response', plot.type='persp', theta=-40,n.grid=1000, border=NA,xlab="",ylab="",zlab="",ticktype="detailed")
dev.off()

gam_5<-gam(PBD_turn.ses~te(climate_distance1,distance,k=3),data=beta)
tiff(filename = "figure5-5.tiff",width = 1500,height = 1500,units = "px",compression = "lzw",res = 300)
vis.gam(gam_5,type='response', plot.type='persp', theta=-40,n.grid=1000, border=NA,xlab="",ylab="",zlab="",ticktype="detailed")
dev.off()

gam_6<-gam(PBD_nest.ses~te(climate_distance1,distance,k=3),data=beta)
tiff(filename = "figure5-6.tiff",width = 1500,height = 1500,units = "px",compression = "lzw",res = 300)
vis.gam(gam_6,type='response', plot.type='persp', theta=-40,n.grid=1000, border=NA,xlab="",ylab="",zlab="",ticktype="detailed")
dev.off()
```

**Part5.5: Plotting elevational connectivity**  

* For real sampling data
```{r}
require(mgcv)
require(ggplot2)
require(gridExtra)
mytheme<-theme(axis.title=element_text(size=15, lineheight=.9, family="Helvetica",face="bold", colour="black"))+theme(axis.text=element_text(size=12, lineheight=.9,family="Helvetica",face="bold", colour="black"))
a<-read.csv("summary_300.csv")
tbd<-ggplot(aes(x=ele_ave, y=tbd), data=a) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr",k=3))+xlab("Average elevation (m)")+ylab("Taxonomic beta")+ylim(-4.5,4.5)
pbd<-ggplot(aes(x=ele_ave, y=pbd), data=a) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr",k=3))+xlab("Average elevation (m)")+ylab("phylogenetic beta")+ylim(-3,3)
cost<-ggplot(aes(x=ele_ave, y=log(cost_dis)), data=a) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr",k=3))+xlab("Average elevation (m)")+ylab("Cost distance(log)")
geo<-ggplot(aes(x=ele_ave, y=geo_dis), data=a) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr",k=3))+xlab("Average elevation (m)")+ylab("Geographic distance(km)")
tiff(filename = "figure8_300-1.tiff",width = 2000,height = 1800,units = "px",compression = "lzw",res = 300)
grid.arrange(cost,geo,tbd,pbd,nrow=2)
dev.off()

tbd_cost<-ggplot(aes(x=log(cost_dis), y=tbd), data=a) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr",k=3))+xlab("Cost distance(log)")+ylab("Taxonomic beta")+ylim(-4.5,4.5)
pbd_cost<-ggplot(aes(x=log(cost_dis), y=pbd), data=a) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr",k=3))+xlab("Cost distance(log)")+ylab("Phylogenetic beta")+ylim(-3,3)
tiff(filename = "figure7.tiff",width = 2000,height = 900,units = "px",compression = "lzw",res = 300)
grid.arrange(tbd_cost,pbd_cost,nrow=1)
dev.off()

tbd_geo<-ggplot(aes(x=geo_dis, y=tbd), data=a) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr",k=3))+xlab("Geographic distance (km)")+ylab("Taxonomic beta")+ylim(-4.5,4.5)
pbd_geo<-ggplot(aes(x=geo_dis, y=pbd), data=a) +geom_point() +geom_smooth(se=T, method='gam', formula=y~s(x, bs="cr",k=3))+xlab("Geographic distance (km)")+ylab("Phylogenetic beta")+ylim(-3,3)
tiff(filename = "figure7-2.tiff",width = 2000,height = 900,units = "px",compression = "lzw",res = 300)
grid.arrange(tbd_geo,pbd_geo,nrow=1)
dev.off()

tiff(filename = "figure7-500.tiff",width = 2000,height = 1800,units = "px",compression = "lzw",res = 300)
grid.arrange(tbd_cost,pbd_cost,tbd_geo,pbd_geo,nrow=2)
dev.off()
```